---
title: "sockult_24"
author: "Anne Christine Vig Jensen"
date: '`r Sys.Date()`'
output: html_document
---

#setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages}
library(tidyverse)
library(gridExtra)
library(knitr)
install.packages("kableExtra")
library(kableExtra)
```

```{r load files}
setwd("/Users/annechristinevig/Desktop/sockult_24")

df_blinding <- read.csv("blinding_plot.csv")
df_no_int <- read.csv("no_int_plot.csv")
df_parental <- read.csv("parental_plot.csv")
df_quota <- read.csv("quota_plot.csv")
#df_vali <- read.csv("vali_plot.csv")
```

```{r renaming loop}
# List of data frame names
df_names_org <- c("df_blinding", "df_no_int", "df_parental", "df_quota")

# Loop over each data frame name to rename the first column to 'id'
for(df_name in df_names_org) {
  # Get the data frame
  df <- get(df_name)
  
  # Rename the first column to 'id'
  colnames(df)[1] <- "id"
  
  # Rename the 3rd column to 'month'
  colnames(df)[3] <- "month"
  
  #Removing 'levels" from 'positions', and converting levels into a numeric column containing     only the numbers of levels 
  df$position <- as.numeric(gsub("Level ", "", as.character(df$position)))

  # Assign the modified data frame back to its original name
  assign(df_name, df)
}
```
 
# 5 year difference 

##From month/tick 59 = 5 years 
(from python = 0 index)
```{r loop 5th year}
# loop for creating datasets  with data from the 5th year 
for(df_name in df_names_org) {

  # Get the data frame
  df <- get(df_name)

  # Filter the data frame to include only rows where 'month' is 59 
  filtered_df <- df %>% filter(month == 59)
  
  #Filtering positions so we get the three highest levels (1,2,3)
  filtered_df <- filtered_df %>% filter(position <= 3)

  # Create a new name ending with "_5y"
  new_name <- paste0(df_name, "_5y")
  
  # Assign the filtered data frame to the new name
  assign(new_name, filtered_df)
}
```

##subtracting percentage women from no interventions with intervensions

looping over dataframes with 5ys, subtract df_no_inv_5ys$percent_women with df's$percent_women to get difference. then save as _5ys_sub
```{r loop no intervention 5 years, subtracted}

df_names_5y <- c("df_blinding_5y", "df_no_int_5y", "df_parental_5y", "df_quota_5y")

# Loop over each 5y data frame name
for(df_name_5y in df_names_5y) {
  
  # Skip the no intervention df 
  if (df_name_5y == "df_no_int_5y") {
    next
  }
  
  # Get the data frame
  df <- get(df_name_5y)
  
  # Subtract df_no_int_5y$percent_women from df$percent_women
  df$percent_wom <- df$percent_wom - df_no_int_5y$percent_wom
  #df$percent_wom <- (df$percent_wom - df_no_int_5y$percent_wom)/ df_no_int_10y$percent_wom *100
  
  # Assign the modified data frame back to its original name with "_sub" suffix
  assign(paste0(df_name_5y, "_sub"), df)
}
```

## Now with 10 years 
```{r 10 years}
df_names_org

# loop for creating datasets only with data from the 10th year
for(df_name in df_names_org) {

  # Get the data frame
  df <- get(df_name)

  # Filter the data frame to include only rows where 'month' is 120
  filtered_df <- df %>% filter(month == 119)
  
  #Filtering positions 
  filtered_df <- filtered_df %>% filter(position <= 3)

  # Create a new name ending with "_10y"
  new_name <- paste0(df_name, "_10y")
  
  # Assign the filtered data frame to the new name
  assign(new_name, filtered_df)
}
```

```{r loop no intervention 10 years, subtracted}
df_names_10y <- c("df_blinding_10y", "df_no_int_10y", "df_parental_10y", "df_quota_10y")

# Loop over each 5y data frame name
for(df_name_10y in df_names_10y) {

  # Get the data frame
  df <- get(df_name_10y)
  
  # Subtract df_no_int_5y$percent_women from df$percent_women
  df$percent_wom <- df$percent_wom - df_no_int_10y$percent_wom
  
  # Assign the modified data frame back to its original name with "_sub" suffix
  assign(paste0(df_name_10y, "_sub"), df)
}
```

# Plotting 

quota plotting 
## Making dataset for plotting
```{r}
quota_10_plot <- ggplot(df_quota_10y_sub, aes(x = position, y = percent_wom)) + 
  geom_bar(stat = "identity") + 
  scale_x_continuous(breaks = c(1, 2, 3), labels = c("C-suite", "Senior Vice President", "Vice President"))+
  labs(title = "Gender quota", subtitle = "After 10 years") + 
  xlab("Level") + 
  ylab("Percentage Women \n subtracted with no intervention") + 
  ylim(-1, 6) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) # Adjust x-axis label orientation
```

```{r}
blinding_10_plot <- ggplot(df_blinding_10y_sub, aes(x = position, y = percent_wom)) + 
  geom_bar(stat = "identity") + 
  scale_x_continuous(breaks = c(1, 2, 3), labels = c("C-suite", "Senior Vice President", "Vice President"))+
  labs(title = "Blinding", subtitle = "After 10 years") + 
  xlab("Level") + 
  ylab("Percentage Women \n subtracted with no intervention") + 
  ylim(-1, 6) +  
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) # Adjust x-axis label orientation
```

```{r}
parental_10_plot <- ggplot(df_parental_10y_sub, aes(x = position, y = percent_wom)) + 
  geom_bar(stat = "identity") + 
  scale_x_continuous(breaks = c(1, 2, 3), labels = c("C-suite", "Senior Vice President", "Vice President"))+
  labs(title = "50/50 Parental Leave", subtitle = "After 10 years") + 
  xlab("Level") + 
  ylab("Percentage Women \n subtracted with no intervention") + 
  ylim(-1, 6) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) # Adjust x-axis label orientation
```

```{r}
grid.arrange(quota_10_plot, blinding_10_plot, parental_10_plot, nrow=1, ncol=3) 
```

## creating table of output 

We'll use
df_blinding_10y_sub
df_parental_10y_sub
df_quota_5y_sub

```{r}
# Combine the three dataframes into one
combined_df <- bind_rows(
  mutate(df_blinding_10y_sub, dataset = "Blinding"),
  mutate(df_parental_10y_sub, dataset = "Parental"),
  mutate(df_quota_10y_sub, dataset = "Quota")
)

combined_df
# Group by position and dataset, then summarize to calculate mean percentage_wom
summary_table <- combined_df %>%
  group_by(position, dataset) %>%
  summarize(mean_percentage_wom = round(mean(percent_wom), 2))

# Reshape the table to have position as rows and dataset as columns
summary_table_wide <- summary_table %>%
  pivot_wider(names_from = dataset, values_from = mean_percentage_wom)

# Generate the pretty table using kable and add grid and space between values
summary_table_kable <- kable(summary_table_wide, caption = "Mean Percentage of Women by Position subtracted with no intervention", align = "c") %>%
  kable_styling(full_width = FALSE) 
 
summary_table_kable
```
# Now with relative difference 

```{r}
# Combine the three dataframes into one
combined_df2 <- bind_rows(
  mutate(df_blinding_10y_sub, dataset = "Blinding"),
  mutate(df_parental_10y_sub, dataset = "Parental"),
  mutate(df_quota_5y_sub, dataset = "Quota")
)

# Group by position and dataset, then summarize to calculate mean percentage_wom
summary_table2 <- combined_df %>%
  group_by(position, dataset) %>%
  summarize(mean_percentage_wom = round(mean(percent_wom), 2))

# Reshape the table to have position as rows and dataset as columns
summary_table_wide <- summary_table %>%
  pivot_wider(names_from = dataset, values_from = mean_percentage_wom)

# Generate the pretty table using kable and add grid and space between values
summary_table_kable <- kable(summary_table_wide, caption = "Mean Percentage of Women by Position subtracted with no intervention", align = "c") %>%
  kable_styling(full_width = FALSE) 
 
summary_table_kable
```

```{r}
# Function to calculate relative difference
calculate_relative_difference <- function(df_intervention, df_no_intervention) {
  relative_diff <- (df_intervention - df_no_intervention) / df_no_intervention * 100
  return(round(relative_diff, 2))
}

# Calculate relative differences for each intervention
relative_diff_blinding <- calculate_relative_difference(df_blinding_10y, df_no_int_10y)
relative_diff_quota <- calculate_relative_difference(df_quota_10y, df_no_int_10y)
relative_diff_parental <- calculate_relative_difference(df_parental_10y, df_no_int_10y)

# Create dataframe for the table
top_row <- c("Blinding", "Parental Leave", "Quota")
second_row <- rep(c("1", "2", "3"), 3)
third_row <- combined_df$percent_wom
fourth_row <- c(relative_diff_blinding$percent_wom, relative_diff_parental$percent_wom, relative_diff_quota$percent_wom)

table_data <- data.frame(Intervention = rep(top_row, each = 3),
                         Level = second_row,
                         Mean_Percentage_Wom = third_row,
                         Relative_Difference = fourth_row)

# Generate the pretty table using kable
table_kable <- kable(table_data, caption = "Mean Percentage of Women subtracted with No Intervention and Relative Difference to No Intervention - After 10 years", align = "c") %>%
  kable_styling(full_width = FALSE)

table_kable   
``` 


```{r}

```


